---
title: "4kpbmc"
author: "Denny Shin"
date: "2018-09-26"
output: workflowr::wflow_html
---

```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "C:/Users/Denny/Dropbox/Uni/Research Project/Learning-Thoughts/analysis/")
```

# **Introduction**

4k PBMC single cell analysis

I will follow along with Seurat

# **Setup the Seurat Object**

```{r}
library(Seurat)
library(dplyr)

pbmc.data = Read10X(data.dir = "../data/4k PBMCs from a Healthy Donor/pbmc4k_filtered_gene_bc_matrices/filtered_gene_bc_matrices/GRCh38/")

dense.size = object.size(x =  as.matrix(x = pbmc.data))
dense.size

sparse.size = object.size(x = pbmc.data)
sparse.size

dense.size/sparse.size

pbmc <- CreateSeuratObject(raw.data = pbmc.data, min.cells = 3, min.genes = 200, project = "10X_4kPBMC")
```

# **QC**

#### **filter poor quality cells**

```{r}
mito.genes <- grep(pattern = "^MT-", x = rownames(x = pbmc@data), value = TRUE)
percent.mito <- Matrix::colSums(pbmc@raw.data[mito.genes, ])/Matrix::colSums(pbmc@raw.data)

pbmc <- AddMetaData(object = pbmc, metadata = percent.mito, col.name = "percent.mito")
VlnPlot(object = pbmc, features.plot = c("nGene", "nUMI", "percent.mito"), nCol = 3)

par(mfrow = c(1, 2))
GenePlot(object = pbmc, gene1 = "nUMI", gene2 = "percent.mito")
GenePlot(object = pbmc, gene1 = "nUMI", gene2 = "nGene")
```

from the graphs, I decided to filter out cells with 10 or more percentage of mitochondrial genes

also cells with unique gene counts over 4000

```{r}
pbmc <- FilterCells(object = pbmc, subset.names = c("nGene", "percent.mito"), low.thresholds = c(200, -Inf), high.thresholds = c(4000, 0.10))
```

#### **Normalising the data**

```{r}
pbmc <- NormalizeData(object = pbmc, normalization.method = "LogNormalize", scale.factor = 10000)
```

# **Detection of variable genes across the single cells**

The parameters chosen here should most likely be similar to the Seurat tutorial but there may be some things I am missing. What are some good reasons to help decide on good cutoff values?

```{r}
pbmc <- FindVariableGenes(object = pbmc, mean.function = ExpMean, dispersion.function = LogVMR, x.low.cutoff = 0.0125, x.high.cutoff = 3, y.cutoff = 0.5)

length(x = pbmc@var.genes)
```

# **Scaling data and removing unwanted sources of variation**

```{r}
pbmc <- ScaleData(object = pbmc, vars.to.regress = c("nUMI", "percent.mito"))
```

# **Perform linear dimensional reduction**

```{r}
pbmc <- RunPCA(object = pbmc, pc.genes = pbmc@var.genes, do.print = TRUE, pcs.print = 1:5, genes.print = 5)
```

```{r}
VizPCA(object = pbmc, pcs.use = 1:2)

VizPCA(object = pbmc, pcs.use = 1:2, num.genes = 10)
```


```{r}
PCAPlot(object = pbmc)
```

We can notice 2 or maybe 3 different cell types??