---
title: "workflowr"
author: "Denny Shin"
date: "2018-07-24"
output: workflowr::wflow_html
---

## **Introduction**

How to use workflowr. Specifically on how to create and maintain the website.


## **Setup and Installation**

1. Install [Rstudio](www.rstudio.com)

2. Install workflowr from CRAN:


```{r eval=FALSE}
install.packages("workflowr")
```

## Starting a new project

1. Use the workflowr library

```{r eval=FALSE}
library("workflowr")

```

2. Configure git (only need to do once per computer)

```{r eval=FALSE}
wflow_git_config(user.name = "Your name", user.email = "email@domain.com")
```

**Note: user.name does not need to match github username.**

3. Start a new project

```{r eval=FALSE}
wflow_start("project_name")
```

4. Build site

```{r eval=FALSE}
wflow_build()
```

5. Publish site

```{r eval=FALSE}
wflow_publish("files", "comment")
```

6. Create a new repository on github

7. Set the origin to the repository

```{r eval=FALSE}
wflow_git_remote("origin", "username", "project_name")
```

**Note: "origin" can be anything you want. "username" must be your exact github username. "project_name" should be the name of your newly created repository.**

8. Push to git

```{r eval=FALSE}
wflow_git_push()
```


## **Making edits**

To update your project follow these steps:

1. Build the site

```{r eval=FALSE}
wflow_build()
```

This builds the site. You can stop here if you just want to preview your changes.

2. Publish the site

```{r eval=FALSE}
wflow_publish("files", "comments")
```

This publishes your changes. It will not yet be seen on the github page.

To publish multiple files inside a folder quickly:

```{r eval=FALSE}
"analysis/*Rmd"
```

will include all files inside analysis with .Rmd extension

3. Push to git

First, make sure that you set your origin for this project first.

```{r eval=FALSE}
wflow_git_push()
```

This will push the published site to the github page. It usually takes a little time to go through.

```{r eval=FALSE}
wflow_git_push(dry_run=TRUE)
```
will show what changes will be made but not actually push to git.

```{r eval=FALSE}
wflow_git_push(republish=TRUE)
```
will republish all html pages.


## **Creating a New Page**

```{r eval=FALSE}
wflow_open("file")
```

This normally opens a .Rmd file but if the file does not exist then it will be created for you. Make sure to give its directory and extension not just the file name.
